\chapter{Acknowledgements}\label{chap:acknowledgements}
\enlargethispage{2ex}
\vspace*{-2pt}
\thispagestyle{empty}

The first thank goes to the amazing supervisors of my phd,  Jan Martin Pawlowski, Monica Dunford and Hans-Christian Schultz-Coulon, for their support, the supervision and the scientific discussions.

\medskip

I'm obviously grateful to the Heidelberg University and the Max Planck Institute for paying my rent and giving me the opportunity of fulfilling my dream of getting a phd and do research.

\medskip

I'm grateful to the referees of this thesis and the members of my defence committee Jan Martin Pawlowski, Monica Dunford, Fred Hamprecht and Lorenzo Masia for wasting a morning of their life to listen to me.

\medskip

Secondly, a huge thanks goes to my phd-siblings, the postdocs, students, visitors and all the amazing people I met along the way, Theo, Tanmoy, Ruth, Ramon, all the Sebastians, Sascha, Patrick, Peter, Nina, Natalie, Nastia, Manuel, Jennifer, Luca, Lynton, the Lennarts, Ilaria, Gonzalo, Emma, Diego, Bob, Barry, Armand, Anke, Michel (list is in strict order of importance). Please have mercy of me, if I forgot you it was probably not on purpose (probably). Also, if you expected personalised greetings, well suck on that, I have too much stuff to do these days.

\medskip

I'm extremely grateful to Ullrich Köthe, Gregor Kasieczka, Simone Marzani, Benjamin Nachman and Michael Spannowsky, the incredible scientists I had the opportunity to (at least partially) work with, and most of all learn from. A special thank of course goes to all the people I directly worked with, Ramon, Lynton, Armand, Manuel and Michel.

\medskip

A special thanks goes to the proof-readers of the thesis Stefano, Peter, Ramon and Michel.

\medskip

Whenever I felt hopeless, I could always count on amazing friends, Ante, Elena, Elisa, Franzo, Giulia V., Jens, Manto, the Minuters, Minuti, Nicola, Nigel, Peter, Pischi, Porots, Princess, Ramon, Verra and Michel (again in strict order of importance).

\medskip

I would never have made it without the support of my family, my parents Annalaura and Benedetto, Ginger, my brother Simone, Krystine and my wonderful niece Aurora. A kind and warm thank goes to Giulia's family, to Alvaro, Elena, Franca, Fuffino, Ester and Federica and to Mirko.

\medskip

Finally, the biggest, warmest thank goes to my better half, the umami of my life, the kimchi in my pancakes, the guanciale in my carbonara: my dear Giulia, without whom I would only be a fish out of water.

